Portfolio conservation of metapopulations\\under climate change

### 2013-08-27 inst/ms/ms.tex
Add notes from Nick

\begin{itemize}
\item
  The introduction may be a bit literature heavy. (We also need to cut 11 references to get to 50.)
\item
  The main message may be a bit repetitive throughout.
\item
  I wish I didn't have so many paragraphs with numbered lists, but am struggling to work around that.
\item
  I think there is room for expansion of the discussion (we still have \textasciitilde{}500 words to play with). The discussion could benefit from bringing in more concrete examples of how this ties in with PNW salmon.
\item
  The supplementary figures and captions aren't finished but should be quick to generate.
\item
  I will write a short vignette describing how to use the R package like I did for the Methods in Ecology and Evolution paper.
\item
  I will submit the \texttt{.pdf} version; the \texttt{.docx} version is for you to edit with Track Changes, if you'd like. Only the \texttt{.pdf} version contains the figures and if you can't see the equations in the \texttt{.docx} version (Andy?) then see the \texttt{.pdf} version.
\item
  We still need to discuss authorship and order of authorship.
\end{itemize}

>>>>

\begin{itemize}
\item
  The introduction may be a bit literature heavy. (We also need to cut 11 references to get to 50.)
\item
  The main message may be a bit repetitive throughout.
\item
  I wish I didn't have so many paragraphs with numbered lists, but am struggling to work around that.
\item
  I think there is room for expansion of the discussion (we still have \textasciitilde{}500 words to play with). The discussion could benefit from bringing in more concrete examples of how this ties in with PNW salmon and I welcome your ideas here. If we have space we could also discuss our results in the context of response diversity literature.
\item
  The supplementary figures and captions aren't finished but should be quick to generate.
\item
  I will write a short vignette describing how to use the R package like I did for the Methods in Ecology and Evolution paper.
\item
  I will submit the \texttt{.pdf} version; the \texttt{.docx} version is for you to edit with Track Changes, if you'd like. Only the \texttt{.pdf} version contains the figures and if you can't see the equations in the \texttt{.docx} version (Andy?) then see the \texttt{.pdf} version.
\item
  We still need to discuss authorship and order of authorship.
\item
  Notes from Nick: (1) add something about how many of these concepts are key elements of conservation ecology, but they haven't been tested quantitatively before, (2) consider flipping the discussion around so the broad elements come first and the salmon applications come near the end, (3) consider sticking with ``one half/other half'', or ``lower half/upper half''. If lower/upper, need to explain reasoning.
\end{itemize}
